Parsing Postfix log files

### 2008-05-01 doc/logparser-background.tex
Added summary table to other parsers' conclusion. Some more details about AWStats. Started testing LMA.
Updates after checking results from LMA.

Parsing in \LMA{} requires major changes to the code to parse new log lines
or extract additional data.  It does not appear to deal with any of the
complications discussed in \sectionref{complications} (initial
complications) and \sectionref{additional complications} (additional
complications).  It does not differentiate between different types of
rejections, so it is not suitable for the purposes of this project; the
data about which restriction caused the rejection is discarded, whereas an
important goal of this project is to retain that data to aid optimisation
and evaluation of Postfix restrictions.  \LMA{} fails to parse Postfix log
files generated on Solaris hosts because the fields added automatically
differ from those added on Linux hosts; logs from Solaris hosts (and
possibly other operating systems) thus require preprocessing before parsing
by \LMA{}.

>>>>

Parsing in \LMA{} requires major changes to the code to parse new log lines
or extract additional data.  It does not appear to deal with any of the
complications discussed in \sectionref{complications} (initial
complications) and \sectionref{additional complications} (additional
complications).  It does not differentiate between different types of
rejections, so it is not suitable for the purposes of this project; the
data about which restriction caused the rejection is discarded, whereas an
important goal of this project is to retain that data to aid optimisation
and evaluation of Postfix restrictions.  \LMA{} fails to parse Postfix log
files generated on Solaris hosts because the fields added automatically
differ from those added on Linux hosts; logs from Solaris hosts (and
possibly other operating systems) thus require preprocessing before parsing
by \LMA{}.  Once the preprocessing has been performed on the
\numberOFlogFILES{} test log files \LMA{} parses the log files without
complaint, though it does produce 32 entries in its output file for every
rejection in the input log file; it also missed some 40\% of delivered
mail.  Once these glaring deficiencies were discovered the author did not
spend more time checking the results.

### 2008-05-01 doc/logparser-other-parsers-review.tex
Updates after checking results from LMA.

\begin{table}[ht]
\begin{tabular}{l|l|l|l|l}
    Parser              & Parsed     & Data        & Custom        & Compressed \\
                        & test logs? & store?      & reports?      & logs       \\
    \hline                                                                      \\
    Pflogsumm           & Yes        & No          & No            & No         \\
    Sawmill             & Yes        & Yes         & Searches      & Partially  \\
    Splunk              & Yes        & Yes         & Searches      & Yes        \\
                        &            &             & \& reports    &            \\
    Isoqlog             & No         & Yes         & No            & No         \\
    AWStats             & Partially  & Yes         & Partially\dag & Yes        \\
    Throughput monitor  & N/A        & No          & No            & No         \\
    Anteater            & No         & No          & No            & No         \\
    YAALA               & No         & Yes\ddag    & Yes           & No         \\
    Logparser/Lire      & Yes        & Yes         & Yes           & Yes        \\
    Logrep              & No         & Yes         & No            & No         \\
    Log Mail Analyser   & Yes        & Yes         & Partially     & No         \\ 
    \parsername{}       & Yes        & Yes\dag\dag & No            & Yes        \\
\end{tabular}

>>>>

\begin{table}[ht]
\begin{tabular}{l|l|l|l|l}
    Parser              & Parsed     & Data        & Custom        & Compressed \\
                        & test logs? & store?      & reports?      & logs       \\
    \hline                                                                      \\
    Pflogsumm           & Yes        & No          & No            & No         \\
    Sawmill             & Yes        & Yes         & Searches      & Partially  \\
    Splunk              & Yes        & Yes         & Searches      & Yes        \\
                        &            &             & \& reports    &            \\
    Isoqlog             & No         & Yes         & No            & No         \\
    AWStats             & Partially  & Yes         & Partially\dag & Yes        \\
    Throughput monitor  & N/A        & No          & No            & No         \\
    Anteater            & No         & No          & No            & No         \\
    YAALA               & No         & Yes\ddag    & Yes           & No         \\
    Logparser/Lire      & Yes        & Yes         & Yes           & Yes        \\
    Logrep              & No         & Yes         & No            & No         \\
    Log Mail Analyser   & No         & Yes         & Partially     & No         \\ 
    \parsername{}       & Yes        & Yes\dag\dag & No            & Yes        \\
\end{tabular}
